S. Bikulcius Thesis: Analysis

### 2024-03-08 S. Bikulcius Thesis/analysis_report.Rmd
small changes to rmd
listener descriptives

library(tidyverse)
library(rio)
library(glmmTMB)
library(janitor)
library(ggpubr)
library(patchwork)

@@

# Participant Demographics

```{r pressure, echo=FALSE}

plot(pressure)

@@

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

# Loading needed packages

library(tidyverse)
library(rio)
library(glmmTMB)
library(janitor)
library(ggpubr)
library(patchwork)
library(gt)
library(gtsummary)
library(ggridges)

# Loading saved data

## Pupil Dilation Data

pupil <- rio::import("Data/cleaned_data.csv") |>
  # Getting Analysis Window
  dplyr::filter(timebins >= 500) |>
  dplyr::group_by(subject, trial) |>
  dplyr::filter(timebins <= max(timebins) - 2000) |>
  dplyr::ungroup() |>
  # Getting Peak Pupil Dilation Value
  dplyr::group_by(subject, trial, speaker, code, rep_acc) |>
  dplyr::summarize(peak_pupil = max(pupil.binned)) |>
  dplyr::ungroup()

## Cognitive Data

cog <- rio::import("Data/cleaned_cog_data.csv")

## Listener Demographics

demo <- rio::import("Data/cleaned_listener_demo.csv") |>
  dplyr::mutate(gender = factor(gender, levels = c("Man", "Woman", "Nonbinary", "Questioning", "Prefer not to answer")),
                ethnicity = factor(ethnicity, levels = c("Hispanic/Latino(a/e)", "Not Hispanic/Latino(a/e)", "Prefer not to answer")),
                race = factor(race, levels = c("white/Caucasian", "Black/African American", "Asian/Asian American",
                                               "Native Hawaiian or Other Pacific Islander", "Native American or Alaska Native",
                                               "Biracial or Multiracial", "Prefer not to answer", "Race not listed")),
                native_lang = factor(native_lang, c("American English", "Not American English")))
```

# Listener Characteristics

## Demographics

The participant age range is from 18 to 39 years old. All participants reported they were fluent in English. However, two participants indicated that their native language is not American English. Their native languages were Spanish and Turkish respectively.

demo_table <- demo |>
  dplyr::select(age, gender, ethnicity, race, native_lang) |>
  tbl_summary(type = list(age ~ "continuous",
                          gender ~ "categorical",
                          ethnicity ~ "categorical",
                          race ~ "categorical",
                          native_lang ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} ({p}%)"),
              digits = list(everything() ~ c(2)),
              label = list(age ~ "Age",
                           gender ~ "Gender",
                           ethnicity ~ "Ethnicity",
                           race ~ "Race",
                           native_lang ~ "Native Language")) |>
  as_gt()

demo_table

demo_table |>
  gt::gtsave("Tables/demo_table.html")

@@

## Cognition

### Descriptives

cog_table <- cog |>
  dplyr::select(-subject) |>
  # Just using the age-corrected scores
  dplyr::select(ends_with("_c")) |>
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(everything() ~ c(2)),
              label = list(list_sort_c ~ "Working Memory",
                           flanker_c ~ "Inhibitory Control",
                           card_sort_c ~ "Cognitive Flexibility",
                           pattern_c ~ "Processing Speed")) |>
  as_gt()

cog_table

@@

### Distribution

cog |>
  dplyr::select(subject, ends_with("_c")) |>
  tidyr::pivot_longer(cols = list_sort_c:pattern_c,
                      names_to = "cog_measure",
                      values_to = "score") |>
  ggplot() +
  aes(x = score,
      y = cog_measure,
      color = cog_measure,
      fill = cog_measure) +
  geom_density_ridges(jittered_points = T,
                      position = position_points_jitter(width = 0.05, height = 0),
                      point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.5) +
  theme_classic()
